Different populations agree on which moral arguments underlie which opinions

### 2021-02-16 rscripts/manuscript-results.Rmd
reduce out.width

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 7.1, fig.height = 3.15,
                      dpi = 300, dev="jpeg", tidy = TRUE)

@@

```{r fig.width=3.35, fig.height=2.76, fig.cap="Figure 4. Scatter plots of 1,728 argument applicability scores (8 types of arguments by 216 moral opinions), measured in different groups in the United Kingdom: women vs. men (A),  younger vs. older (B), right-wing vs. left-wing (C), and higher vs. lower education (D). Regression lines in blue and reference lines for perfect agreement in black."}

>>>>

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 7.1, fig.height = 3.15, 
                      out.width = "60%", fig.align = 'center',
                      dpi = 300, dev="jpeg", tidy = TRUE)

@@

```{r fig.width=3.35, fig.height=2.76, out.width = "40%", fig.cap="Figure 4. Scatter plots of 1,728 argument applicability scores (8 types of arguments by 216 moral opinions), measured in different groups in the United Kingdom: women vs. men (A),  younger vs. older (B), right-wing vs. left-wing (C), and higher vs. lower education (D). Regression lines in blue and reference lines for perfect agreement in black."}
